---
title: "SMTData"
author: "Jackson Balch"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(caret)
library(mlbench)
library(npreg)
library(glmnet)
library(MLmetrics)
set.seed(69)
```

## Data Load
```{r DataLoad}
dat <- read.csv('SBSimple.csv')
dat <- na.omit(dat)
sample <- sample(c(T, F), nrow(dat), replace = T, prob = c(0.8, 0.3))
train <- dat[sample, ]
train <- train %>%
  select(popTime, exchange, timeOfThrow, timeToPlate, leadoff, rDist2B, maxSpeed, ball_x, ball_y, ball_z, SB)
test <- dat[!sample, ]
true_train_vals <- test$SB
test <- test %>%
  select(popTime, exchange, timeOfThrow, timeToPlate, leadoff, rDist2B, maxSpeed, ball_x, ball_y, ball_z)
dat <- dat %>%
  group_by(playerAct)


```

## Data compulation
```{r Data comp}
comp_dat <- dat %>%
  mutate(game_play_id = paste(dat$game_str, dat$play_id, sep = "_"))

comp_dat$playerAct <- ifelse(comp_dat$playerAct %in% c("C", "P"), comp_dat$playerAct, "F")
  
comp_dat$popTime <- ifelse(comp_dat$playerAct == "C", comp_dat$popTime, mean(comp_dat$popTime, na.rm = T))

comp_dat$exchange <- ifelse(comp_dat$playerAct == "C", comp_dat$exchange, mean(comp_dat$exchange, na.rm = T))

comp_dat$timeOfThrow <- ifelse(comp_dat$playerAct == "P", mean(comp_dat$timeOfThrow, na.rm = T), comp_dat$timeOfThrow)

comp_dat$timeToPlate <- ifelse(comp_dat$playerAct == "P", comp_dat$timeToPlate,  mean(comp_dat$timeToPlate, na.rm = T))
```

## Modeling
```{r Non-parametric models}

gcv_np_mod <- gsm(SB ~ popTime + exchange + timeOfThrow + timeToPlate + leadoff + rDist2B + maxSpeed + ball_x + ball_y + ball_z, data = train, family = binomial, method = "GCV")

ocv_np_mod <- gsm(SB ~ popTime + exchange + timeOfThrow + timeToPlate + leadoff + rDist2B + maxSpeed + ball_x + ball_y + ball_z, data = train, family = binomial, method = "OCV")

gacv_np_mod <- gsm(SB ~ popTime + exchange + timeOfThrow + timeToPlate + leadoff + rDist2B + maxSpeed + ball_x + ball_y + ball_z, data = train, family = binomial, method = "GACV")

acv_np_mod <- gsm(SB ~ popTime + exchange + timeOfThrow + timeToPlate + leadoff + rDist2B + maxSpeed + ball_x + ball_y + ball_z, data = train, family = binomial, method = "ACV")

pql_np_mod <- gsm(SB ~ popTime + exchange + timeOfThrow + timeToPlate + leadoff + rDist2B + maxSpeed + ball_x + ball_y + ball_z, data = train, family = binomial, method = "PQL")

aic_np_mod <- gsm(SB ~ popTime + exchange + timeOfThrow + timeToPlate + leadoff + rDist2B + maxSpeed + ball_x + ball_y + ball_z, data = train, family = binomial, method = "AIC")

bic_np_mod <- gsm(SB ~ popTime + exchange + timeOfThrow + timeToPlate + leadoff + rDist2B + maxSpeed + ball_x + ball_y + ball_z, data = train, family = binomial, method = "BIC")

```

```{r lasso}
y <- train$SB
x <- data.matrix(train[c('exchange', 'timeOfThrow', 'timeToPlate', 'leadoff', 'rDist2B', 'maxSpeed', 'ball_x', 'ball_y', 'ball_z')])
x <- scale(x)
 
lambdas <- c()
for (p in 1:100){
  cv <- cv.glmnet(x, y, alpha=1)  
  lambdas <- append(lambdas, cv$lambda)
}
lambda.min <- min(lambdas)
lasso<-train(y= y,
                 x = x,
                 method = 'glmnet', 
                 tuneGrid = expand.grid(alpha = 1, lambda = lambda.min)
               )
coef(lasso$finalModel, lasso$bestTune$lambda)
```

```{r step}
step_data <- as.data.frame(x)
rownames(step_data) <- NULL
step_data$y <- y
simple <- glm(y ~ exchange + timeOfThrow + timeToPlate + leadoff, data = step_data, family = "binomial")
complicated <- glm(y ~., data = step_data, family = "binomial")
step(simple, scope = list(lower=simple, upper=complicated), direction = "both", k=2)
```


```{r ridge}
y <- train$SB
x <- data.matrix(train[c('exchange', 'timeOfThrow', 'timeToPlate', 'leadoff', 'rDist2B', 'maxSpeed', 'ball_x', 'ball_y', 'ball_z')])
x <- scale(x)
 
lambdas <- c()
for (p in 1:100){
  cv <- cv.glmnet(x, y, alpha=1)  
  lambdas <- append(lambdas, cv$lambda)
}
lambda.min <- min(lambdas)
ridge<-train(y= y,
                 x = x,
                 method = 'glmnet', 
                 tuneGrid = expand.grid(alpha = 0, lambda = lambda.min)
               )
coef(ridge$finalModel, ridge$bestTune$lambda)
```
```

```{r makePredicts}


train_res <- train
train_res['ACV'] <- fitted(acv_np_mod)
train_res['AIC'] <- fitted(aic_np_mod)
train_res['BIC'] <- fitted(bic_np_mod)
train_res['GACV'] <- fitted(gacv_np_mod)
train_res['GCV'] <- fitted(gcv_np_mod)
train_res['LASSO'] <- predict(lasso_model, x)
train_res['OCV'] <- fitted(ocv_np_mod)
train_res['PQL'] <- fitted(pql_np_mod)
train_res['RIDGE'] <- predict(ridge_model, x)
summary(acv_np_mod)
summary(aic_np_mod)
summary(bic_np_mod)
summary(gacv_np_mod)
summary(gcv_np_mod)
summary(ocv_np_mod)
summary(pql_np_mod)
predictions <- test
predictions["TRUTH"] <- true_train_vals
predictions["ACV"] <- predict(acv_np_mod, test, type="response")
predictions["AIC"] <- predict(aic_np_mod, test, type="response")
predictions["BIC"] <- predict(bic_np_mod, test, type="response")
predictions["GACV"] <- predict(gacv_np_mod, test, type="response")
predictions["GCV"] <- predict(gcv_np_mod, test, type="response")
predictions["OCV"] <- predict(ocv_np_mod, test, type="response")
predictions["PQL"] <- predict(pql_np_mod, test, type="response")
lm_test <- as.matrix(test)
predictions["LASSO"] <- predict(lasso_model, lm_test, type="response")
predictions["RIDGE"] <- predict(ridge_model, lm_test, type="response")
predictions

```
